Developing a Visual Studio Code Language Support Extension for the Snail Programming Language

### 2023-06-29 paper.tex
feat: update images/ paths in paper.tex

\begin{wrapfigure}{R}{0.3\textwidth}
    \begin{center}
        \includegraphics[height=0.3\textheight]{directory-structure.png}
        \caption{
            \centering 
                The typical directory structure of a VSCode language support extension.
        }
        \label{fig:directory-structure}
    \end{center}
\end{wrapfigure}

@@

\begin{figure}[b]
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{dev-no-highlight-light.png}
            \caption{Developing snail code without syntax highlighting can be a mentally taxing experience.}
            \label{fig:dev-no-highlight}
        \end{center}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{dev-with-highlight-light.png}
            \caption{Syntax highlighting makes developing snail code much easier.}
            \label{fig:dev-with-highlight}
        \end{center}
    \end{subfigure}
    \caption{Demonatrating the benefit of Snail Language Support's syntax highlighting feature.}
    \label{fig:syntax-highlight}
\end{figure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
    \begin{center}
        \includegraphics[width=0.5\textwidth]{language-server.png}
        \caption{
            \centering 
            A development tool will communicate with a language server to display advanced diagnostics.
        }
        \label{fig:language-server}
    \end{center}
\end{wrapfigure}

@@

\begin{figure}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{no-lsp-theory.png}
            \caption{Without the Language Server Protocol, development tool and language server communication can get messy.}
            \label{fig:no-lsp-theory}
        \end{center}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{lsp-theory.png}
            \caption{The Language Server Protocol streamlines the communication between development tools and language servers.}
            \label{fig:lsp-theory}
        \end{center}
    \end{subfigure}
    \caption{Demonatrating the benefit of VS Code's Language Server Protocol.}
    \label{fig:lsp}
\end{figure}

@@

\begin{figure}[t]
    \begin{subfigure}{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{dev-no-diagnostics-light.png}
            \subcaption{
                \centering
                    Developing snail code without realtime error diagnostics can make it difficult to spot syntax errors.
                }
            \label{fig:dev-no-diagnostics}
        \end{center}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{dev-with-diagnostics-light.png}
            \subcaption{
                \centering
                    With Snail Language Support, a developer can spot easily spot syntax errors and fix them before runtime.
                }
            \label{fig:dev-with-diagnostics}
        \end{center}
    \end{subfigure}
    \caption{
        \centering
            Demonstrating the benefit of realtime error diagnostics provided in Snail Language Support.
        }
    \label{fig:dev-diagnostics}
\end{figure}

\begin{wrapfigure}{R}{0.5\textwidth}
    \includegraphics[width=0.5\textwidth]{lsp-sequence.png}
    \caption{
        \centering
            Modelling the interactions between a developer, a VS Code client, and snail language server while a developer opens and modifies a snail file.
    }
    \label{fig:lsp-sequence}
\end{wrapfigure}

@@

\begin{figure}[h]
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \includegraphics[width=\textwidth]{no-dap-theory.png}
        \caption{
            \centering
                Communication between a generic debugger and a development tool is incredibly complicated.
        }
        \label{fig:no-dap-theory}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \includegraphics[width=\textwidth]{dap-theory.png}
        \caption{
            \centering
                With the Debug Adapter Protocol, a development tool can easily communicate with a generic langauge-specific debugger.
        }
        \label{fig:dap-theory}
    \end{subfigure}
    \caption{
        \centering
            Illustrating the benefit of the Debug Adapter Protocol in aiding development tool and debugger communication.
    }
    \label{fig:dap}
\end{figure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
    \begin{center}
        \includegraphics[width=0.5\textwidth]{dap-high-level.png}
        \caption{
            \centering 
            A high-level overview of VS Code, Snail Language Support, and snail debugging communication
        }
        \label{fig:dap-high-level}
    \end{center}
\end{wrapfigure}

@@

\begin{figure}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{centralized-vcs.png}
            \caption{
                \centering 
                A centralized version control system requires developers to submit individual file changes to a shared repository containing the software source code.
            }
            \label{fig:centralized-vcs}
        \end{center}
    \end{subfigure}
    \hspace{0.05\textwidth} 
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{distributed-vcs.png}
            \caption{
                \centering 
                A distributed version control system allows developers to share revised source code repositories directly with eachother, or through a shared server.
            }
            \label{fig:distributed-vcs}
        \end{center}
    \end{subfigure}
    \label{fig:version-control-systems}
\end{figure}

>>>>

\begin{wrapfigure}{R}{0.3\textwidth}
    \begin{center}
        \includegraphics[height=0.3\textheight]{png/directory-structure.png}
        \caption{
            \centering 
                The typical directory structure of a VSCode language support extension.
        }
        \label{fig:directory-structure}
    \end{center}
\end{wrapfigure}

@@

\begin{figure}[b]
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{screenshots/dev-no-highlight-light.png}
            \caption{Developing snail code without syntax highlighting can be a mentally taxing experience.}
            \label{fig:dev-no-highlight}
        \end{center}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{screenshots/dev-with-highlight-light.png}
            \caption{Syntax highlighting makes developing snail code much easier.}
            \label{fig:dev-with-highlight}
        \end{center}
    \end{subfigure}
    \caption{Demonatrating the benefit of Snail Language Support's syntax highlighting feature.}
    \label{fig:syntax-highlight}
\end{figure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
    \begin{center}
        \includegraphics[width=0.5\textwidth]{png/language-server.png}
        \caption{
            \centering 
            A development tool will communicate with a language server to display advanced diagnostics.
        }
        \label{fig:language-server}
    \end{center}
\end{wrapfigure}

@@

\begin{figure}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{png/no-lsp-theory.png}
            \caption{Without the Language Server Protocol, development tool and language server communication can get messy.}
            \label{fig:no-lsp-theory}
        \end{center}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{png/lsp-theory.png}
            \caption{The Language Server Protocol streamlines the communication between development tools and language servers.}
            \label{fig:lsp-theory}
        \end{center}
    \end{subfigure}
    \caption{Demonatrating the benefit of VS Code's Language Server Protocol.}
    \label{fig:lsp}
\end{figure}

@@

\begin{figure}[t]
    \begin{subfigure}{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{screenshots/dev-no-diagnostics-light.png}
            \subcaption{
                \centering
                    Developing snail code without realtime error diagnostics can make it difficult to spot syntax errors.
                }
            \label{fig:dev-no-diagnostics}
        \end{center}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{screenshots/dev-with-diagnostics-light.png}
            \subcaption{
                \centering
                    With Snail Language Support, a developer can spot easily spot syntax errors and fix them before runtime.
                }
            \label{fig:dev-with-diagnostics}
        \end{center}
    \end{subfigure}
    \caption{
        \centering
            Demonstrating the benefit of realtime error diagnostics provided in Snail Language Support.
        }
    \label{fig:dev-diagnostics}
\end{figure}

\begin{wrapfigure}{R}{0.5\textwidth}
    \includegraphics[width=0.5\textwidth]{png/lsp-sequence.png}
    \caption{
        \centering
            Modelling the interactions between a developer, a VS Code client, and snail language server while a developer opens and modifies a snail file.
    }
    \label{fig:lsp-sequence}
\end{wrapfigure}

@@

\begin{figure}[h]
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \includegraphics[width=\textwidth]{png/no-dap-theory.png}
        \caption{
            \centering
                Communication between a generic debugger and a development tool is incredibly complicated.
        }
        \label{fig:no-dap-theory}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \includegraphics[width=\textwidth]{png/dap-theory.png}
        \caption{
            \centering
                With the Debug Adapter Protocol, a development tool can easily communicate with a generic langauge-specific debugger.
        }
        \label{fig:dap-theory}
    \end{subfigure}
    \caption{
        \centering
            Illustrating the benefit of the Debug Adapter Protocol in aiding development tool and debugger communication.
    }
    \label{fig:dap}
\end{figure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
    \begin{center}
        \includegraphics[width=0.5\textwidth]{png/dap-highlevel.png}
        \caption{
            \centering 
            A high-level overview of VS Code, Snail Language Support, and snail debugging communication
        }
        \label{fig:dap-high-level}
    \end{center}
\end{wrapfigure}

@@

\begin{figure}
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{png/centralized-vcs.png}
            \caption{
                \centering 
                A centralized version control system requires developers to submit individual file changes to a shared repository containing the software source code.
            }
            \label{fig:centralized-vcs}
        \end{center}
    \end{subfigure}
    \hspace{0.05\textwidth} 
    \begin{subfigure}[c][][c]{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{png/distributed-vcs.png}
            \caption{
                \centering 
                A distributed version control system allows developers to share revised source code repositories directly with eachother, or through a shared server.
            }
            \label{fig:distributed-vcs}
        \end{center}
    \end{subfigure}
    \label{fig:version-control-systems}
\end{figure}
